---
title: "`r paste0('A run comparison report generated for the provided WEPPcloud runs')`"
date: "`r Sys.Date()`"
output: 
  cleanrmd::html_document_clean:
    css: "styles.css"
    fig_caption: true
    theme: axist
    mathjax: default
    use_fontawesome: true
    toc: true
    toc_float: true
params:
  ws: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
sys.source("weppcloudr_report_functions.R",envir = knitr::knit_global())
```

```{r include=FALSE}
library(tidyverse, quietly = TRUE)
library(cleanrmd, quietly = TRUE)
library(plotly, quietly = TRUE)
library(furrr, quietly = TRUE)
library(janitor, quietly = TRUE)
library(cleanrmd, quietly = TRUE)
library(echarts4r, quietly = TRUE)
library(DT, quietly = TRUE)
library(leaflet, quietly = TRUE)
library(data.table, quietly = TRUE)
library(leafsync, quietly = TRUE)
library(crosstalk, quietly = TRUE)
library(reshape2, quietly = TRUE)
library(jsonlite, quietly = TRUE)
library(tidytext, quietly = TRUE)

```

<!-- ######################### GENERATE REPORT ##################################-->

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# a="[{\"runid\": \"lt_202012_21_Tunnel_Creek_CurCond\", \"cfg\": \"lt-wepp_bd16b69-snow\", \"name\": \"lt_202012_21_Tunnel_Creek_CurCond\", \"scenario\": null, \"location_hash\": \"lofts.pathfinder.careless\"}, {\"runid\": \"lt_202012_21_Tunnel_Creek_SimFire.landisFuels_fut_cli_A2\", \"cfg\": \"lt-fire-future-snow\", \"name\": \"lt_202012_21_Tunnel_Creek_SimFire.landisFuels_fut_cli_A2\", \"scenario\": null, \"location_hash\": \"lofts.pathfinder.careless\"},{\"runid\": \"lt_202012_20_Mill_Creek_CurCond\", \"cfg\": \"lt-wepp_bd16b69-snow\", \"name\": \"lt_202012_20_Mill_Creek_CurCond\", \"scenario\": null, \"location_hash\": \"lofts.pathfinder.careless\"}]"
# 


a = "[{\"runid\": \"lt_202012_10_Snow_Creek_CurCond\", \"cfg\": \"lt-wepp_bd16b69-snow\", \"name\": \"lt_202012_10_Snow_Creek_CurCond\", \"scenario\": null, \"location_hash\": \"blend.swaying.frantically\"},
{\"runid\": \"lt_202012_20_Mill_Creek_CurCond\", \"cfg\": \"lt-wepp_bd16b69-snow\", \"name\": \"lt_202012_20_Mill_Creek_CurCond\", \"scenario\": null, \"location_hash\": \"lofts.pathfinder.careless\"},
{\"runid\": \"lt_202012_5_Dollar_Creek_CurCond\", \"cfg\": \"lt-wepp_bd16b69-snow\", \"name\": \"lt_202012_5_Dollar_Creek_CurCond\", \"scenario\": null, \"location_hash\": \"total.stress.oiled\"},
{\"runid\": \"lt_202012_10_Snow_Creek_SimFire.fccsFuels_obs_cli\", \"cfg\": \"lt-fire-snow.cfg\", \"name\": \"lt_202012_10_Snow_Creek_SimFire.fccsFuels_obs_cli\", \"scenario\": null, \"location_hash\": \"blend.swaying.frantically\"}]"
# print(a)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
runs_info=jsonlite::fromJSON(a) %>% dplyr::mutate(id = row_number()) 


# runs_info = runs_info %>%
#   dplyr::mutate(scenario = dplyr::case_when(is.na(scenario) ~ paste0("scenario_", id),
#                                             TRUE ~ as.character(scenario)))%>% dplyr::select(-id)

runs_info = runs_info %>%
  dplyr::mutate(watershed_id = as.numeric(factor(location_hash)),
    scenario_id = as.numeric(factor(cfg)),
    Watershed = paste0("watershed_", watershed_id),
    scenario = paste0("scenario_", scenario_id))

vec_runids = as.vector(runs_info$runid)

```

#### Runs synthesized

```{r, echo=FALSE,message=FALSE,warning=FALSE}
runs_info %>% dplyr::select(runid, Watershed, scenario) %>% DT::datatable(class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                           scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
                           fillContainer = FALSE))

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
subcatchments = purrr::map_df(vec_runids,read_subcatchments_map)
subcatchments = dplyr::left_join(subcatchments, runs_info, by = c("runid"))

```


### Land Cover & Soils 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
landuse_map= make_leaflet_map_multi(subcatchments, landuse, col_pal_type = "Factor")
soil_map= make_leaflet_map_multi(subcatchments, soil, col_pal_type = "Factor")
texture_map= make_leaflet_map_multi(subcatchments, Texture, col_pal_type = "Factor")
gradient_map= make_leaflet_map_multi(subcatchments, gradient, col_pal_type = "Factor")
leafsync::sync(landuse_map,
               soil_map,
               texture_map,
               gradient_map,
               ncol = 2,
               sync = "all")

```


```{r, echo=FALSE,message=FALSE,warning=FALSE}
### totalwatsed

totalwatseddf = purrr::map_df(vec_runids, process_totalwatsed_map_df)
totalwatseddf = dplyr::left_join(totalwatseddf, runs_info, by ="runid")

totalwatsed_wy_mean_df = totalwatseddf %>%
    dplyr::select(-julian,-year,-Date,-mo,-da, -Watershed, -scenario) %>%
    dplyr::group_by(runid, WY) %>% dplyr::left_join(runs_info, by ="runid")

totalwatsed_wbal = totwatsed_to_wbal_map_dfs(totalwatseddf)
```



<div style="clear: both;"></div>

### Hydrology


#### Watershed water balance 

```{r, echo=FALSE,message=FALSE,warning=FALSE}
totalwatsed_wbal1 = totalwatsed_wbal %>% dplyr::select(-c(`Precipitation (mm)`)) %>%
  dplyr::rename('Precipitation' = 'Rain+Melt (%)')%>% tidyr::pivot_longer(-runid)
```


```{r, echo=FALSE,message=FALSE,warning=FALSE}

totalwatsed_wbal1 =totalwatsed_wbal %>% dplyr::select(-c(`Precipitation (mm)`)) %>%
  dplyr::rename('Precipitation' = 'Rain+Melt (%)')%>% tidyr::pivot_longer(-runid)%>% dplyr::mutate(name = str_replace(name,pattern = "\\([^()]{0,}\\)", ""))

watbal_plt= totalwatsed_wbal1 %>%
    mutate(runid = as.factor(runid),
           name = reorder_within(name, value, runid)) %>%  ggplot(aes(name, value, fill = runid)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~runid, scales = "free",ncol = 2) +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%")) +ggthemes::theme_hc() + ggthemes::scale_fill_hc() +labs(y = "", x = "")+
  theme(legend.position = "none")

ggplotly(watbal_plt)
```

#### Runoff

```{r, echo=FALSE, message=FALSE,warning=FALSE}
 
runoff_cp_df= gen_cumulative_plt_df_map(subcatchments, runoff_mm)
sd_yd_cp_df= gen_cumulative_plt_df_map(subcatchments, Sediment_Yield_kg)
tp_cp_df = gen_cumulative_plt_df_map(subcatchments, Total_Phosphorus_kg)
```

```{r, echo=FALSE, message=FALSE,warning=FALSE}
# Wrap data frame in SharedData
runoff_cp_df = runoff_cp_df %>% 
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F) 
sd_r=  runoff_cp_df %>%
  sf::st_as_sf() %>% 
  sf::st_cast() 
sd_r <- SharedData$new(sd_r)

```

```{r, echo=FALSE, message=FALSE,warning=FALSE}

ggplotly(ggplot() +
  geom_line(data = sd_r$data(), aes(x = cumPercArea, y = cum_runoff_mm, color = Watershed_scenario), size = 1)+ 
  ggthemes::theme_fivethirtyeight()+ ggthemes::scale_color_colorblind() +
    scale_y_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%"))+
    scale_x_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%")))%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = "Runoff (%)"),
                                  xaxis = list(title = "Percent of total hillslope area"))
```
</br></br></br>

```{r, echo=FALSE, message=FALSE,warning=FALSE}
runoff_totals_plt= sd_r$data() %>%as.data.frame() %>% 
  dplyr::group_by(Watershed_scenario) %>%
  dplyr::summarise_at(.vars = "runoff_mm", .funs = sum) %>% 
  ggplot(aes(reorder(Watershed_scenario, runoff_mm),runoff_mm, fill = Watershed_scenario)) +
    geom_col(show.legend = TRUE) +
    coord_flip() +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_hc() +labs(y = "", x = "")+theme(axis.text.y = element_blank())

ggplotly(runoff_totals_plt)%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = ""),
                                  xaxis = list(title = "Total Runoff (mm)"))
```

<br><br><br>

```{r, echo=FALSE, message=FALSE,warning=FALSE}
map_multiplelayers_runoff <- function(df) {
  
  df = df %>% 
    tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F) 
  #number of groups
  n <- n_distinct(df$Watershed_scenario)
  #colorpal
  # pal1 <- colorNumeric("viridis", domain = df$runoff_mm)
  # pal1 <- colorBin("viridis", df$runoff_mm,10, pretty = FALSE)
  
  #base map
  map <- leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron)
  
  k=unique(df$Watershed_scenario)
  
  for (i in k) {
    
    a= df %>% filter(Watershed_scenario == i)
    pal1 <- colorBin("viridis", a$runoff_mm,10, pretty = FALSE)
  
    map <- map %>%
      addPolygons(
        data= a,
        fillColor = ~pal1(runoff_mm),
        weight = 2,
        opacity =1,
        color = "white",
        dashArray = "3",
        fillOpacity = 1,
        group = i,
        popup = ~paste("WeppID:", a$wepp_id,
                                          "<br>",
                                          "Watershed:", a$Watershed,
                                          "<br>",
                                          "Scenario:", a$scenario,
                                          "<br>",
                                          "Runoff (mm):", a$runoff_mm,
                                          "<br>")
        )%>% addLegend("bottomleft",pal = pal1, values = a$runoff_mm)
  }
  #create layer control
  map
  map %>%
    addLayersControl(
      overlayGroups = k,
      options = layersControlOptions(collapsed = FALSE,)) %>%
    hideGroup(k[2:n]) 
}
```


```{r, echo=FALSE, message=FALSE,warning=FALSE}

map_multiplelayers_runoff(sd_r$data())

```


#### Sediments

```{r, echo=FALSE, message=FALSE,warning=FALSE}
 
sd_yd_cp_df= gen_cumulative_plt_df_map(subcatchments, Sediment_Yield_kg)

sd_sed = sd_yd_cp_df %>% sf::st_as_sf() %>% sf::st_cast()%>% 
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F) %>% 
  sf::st_as_sf() %>% 
  sf::st_cast() 
sd_sed <- SharedData$new(sd_sed)

```


```{r, echo=FALSE, message=FALSE,warning=FALSE}

sd_yd_cp_df = sd_sed$data() %>% ggplot(aes(x = cumPercArea)) + 
  geom_line(aes(y = cum_Sediment_Yield_kg, color = Watershed_scenario), size = 1)+ ggthemes::theme_fivethirtyeight()+ ggthemes::scale_color_colorblind() +
    scale_y_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%"))+
    scale_x_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%"))

ggplotly(sd_yd_cp_df)%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = "Sediment Yield (%)"),
                                  xaxis = list(title = "Percent of total hillslope area"))
```


</br></br></br>


```{r, echo=FALSE, message=FALSE,warning=FALSE}
sed_yld_totals_plt= sd_sed$data() %>%as.data.frame() %>% 
  dplyr::group_by(Watershed_scenario) %>%
  dplyr::summarise_at(.vars = "sd_yd_kg_ha", .funs = sum) %>% 
  ggplot(aes(reorder(Watershed_scenario, sd_yd_kg_ha),sd_yd_kg_ha, fill = Watershed_scenario)) +
    geom_col() +
    coord_flip() +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_hc() +labs(y = "", x = "")+theme(axis.text.y = element_blank())

ggplotly(sed_yld_totals_plt)%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = ""),
                                  xaxis = list(title = "Total Sediment Yield (kg/ha)"))
```

#### Phosphorus


```{r, echo=FALSE, message=FALSE,warning=FALSE}
tp_cp_df = gen_cumulative_plt_df_map(subcatchments, Total_Phosphorus_kg)
```

```{r, echo=FALSE, message=FALSE,warning=FALSE}
# Wrap data frame in SharedData
sd_tp= tp_cp_df %>% sf::st_as_sf() %>% sf::st_cast()%>% 
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F) %>% 
  sf::st_as_sf() %>% 
  sf::st_cast() 
sd_tp <- SharedData$new(sd_tp)

```

```{r, echo=FALSE, message=FALSE,warning=FALSE}

tp_yd_cp_df = sd_tp$data() %>% ggplot(aes(x = cumPercArea)) + 
  geom_line(aes(y = cum_Total_Phosphorus_kg, color = Watershed_scenario), size = 1)+ ggthemes::theme_fivethirtyeight()+ ggthemes::scale_color_colorblind() +
    scale_y_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%"))+
    scale_x_continuous(expand = c(0,0),labels = function(x)
        paste0(x * 1, "%"))

ggplotly(tp_yd_cp_df)%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = "Total Phosphorus Yield (%)"),
                                  xaxis = list(title = "Percent of total hillslope area"))
```

</br></br></br>


```{r, echo=FALSE, message=FALSE,warning=FALSE}
tp_yld_totals_plt= sd_tp$data() %>%as.data.frame() %>% 
  dplyr::group_by(Watershed_scenario) %>%
  dplyr::summarise_at(.vars = "tp_kg_ha", .funs = sum) %>% 
  ggplot(aes(reorder(Watershed_scenario, tp_kg_ha),tp_kg_ha, fill = Watershed_scenario)) +
    geom_col() +
    coord_flip() +
  ggthemes::theme_hc() +
  ggthemes::scale_fill_hc() +labs(y = "", x = "")+theme(axis.text.y = element_blank())

ggplotly(tp_yld_totals_plt)%>% layout(legend = list(orientation = "h", y = -0.25,
                                                title=list(text='')),
                                   yaxis = list(title = ""),
                                  xaxis = list(title = "Total Phosphorus Yield (kg/ha)"))
```

### Summary tables

#### Grouped by land use

The table below shows runoff, sediment and phosphorus averages for different land use categories.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
landuse_summary_tab = subcatchments %>% as.data.frame() %>%
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F)%>%  
  dplyr::select(dplyr::any_of(c("Watershed_scenario","landuse","slope",
                              "runoff_mm", "so_ls_kg_ha", 
                              "sd_yd_kg_ha", "tp_kg_ha")))%>%
    plyr::rename( c("landuse" ="Landuse",
                   "slope"="Slope",
                   "so_ls_kg_ha"="Soil Loss (kg/ha)",
                   "sd_yd_kg_ha" ="Sediment Yield (kg/ha)" ,
                   "tp_kg_ha" ="Total Phosphorus (kg/ha)",
                  "runoff_mm"="Runoff (mm)"),warn_missing = FALSE)%>%
    group_by(Watershed_scenario, Landuse) %>% dplyr::summarise_if(is.numeric, list(mean =
                                                                       mean)) %>%
                        dplyr::mutate_if(is.numeric, round, 2)
colnames(landuse_summary_tab) = sapply(strsplit(colnames(landuse_summary_tab), "_mean"), `[[`, 1)

```

```{r, echo=FALSE}
DT::datatable(landuse_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           searching = FALSE,
                           scrollX=400,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```

#### Grouped by soils

The table below shows runoff, sediment and phosphorus averages for different soil types.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
soils_summary_tab = subcatchments   %>% as.data.frame()  %>%
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F)%>%
  dplyr::select(dplyr::any_of(c("Watershed_scenario","soil","slope",
                              "runoff_mm", "so_ls_kg_ha", 
                              "sd_yd_kg_ha", "tp_kg_ha")))%>%
    plyr::rename( c("soil" ="Soil",
                   "slope"="Slope",
                   "so_ls_kg_ha"="Soil Loss (kg/ha)",
                   "sd_yd_kg_ha" ="Sediment Yield (kg/ha)" ,
                   "tp_kg_ha" ="Total Phosphorus (kg/ha)",
                  "runoff_mm"="Runoff (mm)"),warn_missing = FALSE)%>%
    group_by(Watershed_scenario, Soil) %>% dplyr::summarise_if(is.numeric, list(mean =
                                                                       mean)) %>%
                        dplyr::mutate_if(is.numeric, round, 2)

colnames(soils_summary_tab) = sapply(strsplit(colnames(soils_summary_tab), "_mean"), `[[`, 1)

```

```{r, echo=FALSE}
DT::datatable(soils_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=250,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```

#### Grouped by texture

The table below shows runoff, sediment and phosphorus averages for different soil textures.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
texture_summary_tab = subcatchments   %>% as.data.frame() %>%
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F)%>%
  dplyr::select(dplyr::any_of(c("Watershed_scenario","Texture","slope",
                              "runoff_mm", "so_ls_kg_ha", 
                              "sd_yd_kg_ha", "tp_kg_ha")))%>%
    plyr::rename( c("slope"="Slope",
                   "so_ls_kg_ha"="Soil Loss (kg/ha)",
                   "sd_yd_kg_ha" ="Sediment Yield (kg/ha)" ,
                   "tp_kg_ha" ="Total Phosphorus (kg/ha)",
                  "runoff_mm"="Runoff (mm)"),warn_missing = FALSE)%>%
    group_by(Watershed_scenario,Texture) %>% dplyr::summarise_if(is.numeric, list(mean =
                                                                       mean)) %>%
                        dplyr::mutate_if(is.numeric, round, 2)

colnames(soils_summary_tab) = sapply(strsplit(colnames(soils_summary_tab), "_mean"), `[[`, 1)

```

```{r, echo=FALSE}
DT::datatable(texture_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=250,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```

#### Grouped by landuse and soils type and texture.

The table below shows runoff, sediment and phosphorus averages for different combinations of land use categories and soil types.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
both_summary_tab = subcatchments   %>% as.data.frame() %>%
  tidyr::unite("Watershed_scenario",Watershed,scenario,remove = F)%>%
  dplyr::select(dplyr::any_of(c("Watershed_scenario","landuse", "soil","Texture","slope",
                              "runoff_mm", "so_ls_kg_ha", 
                              "sd_yd_kg_ha", "tp_kg_ha")))%>%
    plyr::rename( c("landuse" ="Landuse",
                    "soil" ="Soil",
                   "slope"="Slope",
                   "so_ls_kg_ha"="Soil Loss (kg/ha)",
                   "sd_yd_kg_ha" ="Sediment Yield (kg/ha)" ,
                   "tp_kg_ha" ="Total Phosphorus (kg/ha)",
                  "runoff_mm"="Runoff (mm)"),warn_missing = FALSE)%>%
    group_by(Watershed_scenario,Landuse, Soil,Texture) %>% dplyr::summarise_if(is.numeric, list(mean =
                                                                       mean)) %>%
                        dplyr::mutate_if(is.numeric, round, 2)

colnames(both_summary_tab) = sapply(strsplit(colnames(both_summary_tab), "_mean"), `[[`, 1)

```

```{r, echo=FALSE}
DT::datatable(both_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```