---
title: "A report generated for `r params$proj_run_label` run"
date: "`r Sys.Date()`"
output: 
  cleanrmd::html_document_clean:
    highlight: tango
    css: "styles.css"
    fig_caption: true
    theme: axist
    mathjax: default
    use_fontawesome: true
    toc: true
params:
  proj_runid: default
  proj_config: ""
  proj_run_label: "default"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
sys.source("weppcloudr_report_functions.R",envir = knitr::knit_global())
```

```{r include=FALSE}
library(tidyverse, quietly = TRUE)
library(cleanrmd, quietly = TRUE)
library(plotly, quietly = TRUE)
library(furrr, quietly = TRUE)
library(janitor, quietly = TRUE)
library(htmltools, quietly = TRUE)
library(echarts4r, quietly = TRUE)
library(DT, quietly = TRUE)
library(leaflet, quietly = TRUE)
library(data.table, quietly = TRUE)
library(leafsync, quietly = TRUE)
library(crosstalk, quietly = TRUE)
library(reshape2, quietly = TRUE)
library(sf, quietly = TRUE)

```

<!-- ######################### GENERATE REPORT ##################################-->


```{r, echo=FALSE, message=FALSE, warning=FALSE}
subcatchments = read_subcatchments(params$proj_runid)
```


```{r, echo=FALSE, message=FALSE,warning=FALSE}
lulc_dt = summarize_subcatch_by_var(subcatchments, "landuse")
soil_dt = summarize_subcatch_by_var(subcatchments, "soil")
texture_dt = summarize_subcatch_by_var(subcatchments, "Texture")
gradient_dt = summarize_subcatch_by_var(subcatchments, "gradient")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE}
### totalwatsed

totalwatseddf <- process_totalwatsed(params$proj_runid)

totalwatsed_wy_mean_df = totalwatseddf %>%
          dplyr::select(-dplyr::any_of(c("julian","year","Date","month","day"))) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise(dplyr::across(where(is.numeric), ~mean(.x, na.rm = TRUE)))

totalwatsed_wbal = totwatsed_to_wbal(totalwatseddf)

```

```{r, echo=FALSE,message=FALSE,warning=FALSE}
wshed_area_m2= get_WatershedArea_m2(params$proj_runid)
```


```{r, echo=FALSE, message=FALSE,warning=FALSE}
chanwb = process_chanwb(params$proj_runid,
                  wshed_area_m2)

chanwb_WY_mean = chanwb %>%
          dplyr::select(-Year_chan,
                        -Day_chan,
                        -Chan_ID_chan,
                        -Elmt_ID_chan,
                        -Date) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise(dplyr::across(where(is.numeric), ~mean(.x, na.rm = TRUE)))
```

```{r, echo=FALSE, message=FALSE,warning=FALSE}
yr_min= as.character(min(unique(chanwb$Year_chan)))
yr_max= as.character(max(unique(chanwb$Year_chan)))
```


```{r, echo=FALSE, message=FALSE,warning=FALSE}
ebe = process_ebe(params$proj_runid,
                  yr_min,
                  yr_max)

ebe_WY_mean = ebe %>%
          dplyr::select(-Date,-Day_ebe,-Month_ebe,-Year_ebe) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise(dplyr::across(where(is.numeric), ~mean(.x, na.rm = TRUE)))
```
```{r, echo=FALSE, message=FALSE,warning=FALSE}
merged_daily_df = merge_daily_Vars(totalwatseddf, chanwb, ebe)

merged_WY = dplyr::left_join(totalwatsed_wy_mean_df, chanwb_WY_mean, by = c("WY")) %>%
          dplyr::left_join(ebe_WY_mean, by = c("WY")) %>%
          dplyr::mutate(PercentRunoff = (runoff_mm / (runoff_mm+lateral_flow_mm+baseflow_mm)) * 100,
                        PercentLateral = (lateral_flow_mm / (runoff_mm+lateral_flow_mm+baseflow_mm)) *100,
                        PercentBaseflow = (baseflow_mm / (runoff_mm+lateral_flow_mm+baseflow_mm) )*100)

perc_flow = merged_WY %>%
          dplyr::select(WY, PercentRunoff, PercentLateral, PercentBaseflow)%>%
          dplyr::mutate(
            WY_label = dplyr::case_when(
              is.na(WY) ~ "Unknown",
              WY >= 1000 ~ as.character(WY),
              TRUE ~ paste0("Year ", WY)
            )
          )%>%
          dplyr::mutate(dplyr::across(dplyr::where(is.numeric), round, 1))


```
## About

This report provides detailed graphical output and tabulated summaries of the WEPPcloud watershed run (<span style='color: #6a4c93;'>`r params$proj_runid`</span> run</span>) results. This information is easily downloadable for reports, presentations or other information needs.

### Land Cover & Soils 

Land use, soil type, and corresponding texture and gradient are displayed in the maps below. `r lulc_dt$Landuse[1]` is the dominant land cover type occupying `r lulc_dt$Area[1]`% of the watershed. `r lulc_dt$Landuse[2]` occupies the second largest fraction of the total land cover of the watershed amounting to `r lulc_dt$Area[2]`%. Soils are primarily of `r soil_dt$Soil[1]` and  `r soil_dt$Soil[2]` type and span about `r soil_dt$Area[1]`% and `r soil_dt$Area[2]`% of the watershed area respectively. `r if(texture_dt$Texture[1]=="Refer to the soil file for details") {"<!--"}` A majority (`r texture_dt$Area[1]`%) of the soils in the watershed have `r texture_dt$Texture[1]` texture followed by `r texture_dt$Texture[2]` texture.`r if(texture_dt$Texture[1]=="Refer to the soil file for details"){"-->"}` 
`r gradient_dt$Area[1]`% of the watershed has `r gradient_dt$Gradient[1]` followed by `r gradient_dt$Area[2]`% consisting of `r gradient_dt$Gradient[2]`.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
landuse_map= make_leaflet_map(subcatchments, landuse, col_pal_type = "Factor")
soil_map= make_leaflet_map(subcatchments, soil, col_pal_type = "Factor")
texture_map= make_leaflet_map(subcatchments, Texture, col_pal_type = "Factor")
gradient_map= make_leaflet_map(subcatchments, gradient, col_pal_type = "Factor")
leafsync::sync(landuse_map,
               soil_map, 
               texture_map,
               gradient_map, 
               ncol = 2,
               sync = "all")

```


<div style="clear: both;"></div>

### Climate Summary
```{r, echo=FALSE,message=FALSE,warning=FALSE}
cli_stats = get_cli_summary(params$proj_runid)
```

During the simulation period between water years `r cli_stats$water_year_start` and `r cli_stats$water_year_end`, `r cli_stats$storm_count` recorded events produced an average annual precipitation depth of `r round(cli_stats$mean_annual_precip_mm)` mm. This resulted in an average annual streamflow depth of `r round(cli_stats$mean_annual_streamflow_mm)` mm at the watershed outlet (total precipitation `r round(cli_stats$total_precip_mm)` mm, total streamflow `r round(cli_stats$total_streamflow_mm)` mm).


### Hydrology

```{r, echo=FALSE,message=FALSE,warning=FALSE}
totalwatsed_wbal =totalwatsed_wbal %>% 
  dplyr::filter(variable != "Precipitation (mm)")%>% 
  dplyr::mutate(variable=recode(variable, 'Rain+Melt (%)'='Precipitation (%)')) %>%
  dplyr::filter(variable != "Precipitation (%)") %>%
  dplyr::arrange(-value)
```


#### Watershed water balance 

A large fraction of water was lost to `r tolower(gsub("[(%)]","",totalwatsed_wbal$variable[1]))` amounting  to `r round(totalwatsed_wbal$value[1])`% followed by `r tolower(gsub("[(%)]","",totalwatsed_wbal$variable[2]))` amounting to `r round(totalwatsed_wbal$value[2])`%.  

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.cap=""}
totalwatsed_wbal%>%
            echarts4r::e_charts(variable)  %>%
            echarts4r::e_pie(
                value,
                radius = c("55%", "70%"))%>%
          echarts4r::e_tooltip()%>% e_theme("auritus")%>%
          echarts4r::e_legend(textStyle = list(fontSize = 14))
```


<!-- #### Hillslope water balance   -->

<!-- Figure below shows a long term (simulation period) change in storage for each simulated hillslope in the watershed.   -->

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##switched off in the report asked by Erin.
# watfilepaths <- gethillwatfiles(params$proj_runid)
# future::plan(multisession, workers = 6)
# watbal<- furrr::future_map(watfilepaths, calc_watbal)%>%
#   dplyr::bind_rows() %>%
#   dplyr::mutate_if(is.list, purrr::simplify_all) %>%
#   tidyr::unnest(cols = c("wb", "WeppID"))
# shp <- get_geometry(params$proj_runid)
# Hwatbal_spdf = dplyr::left_join(shp, watbal, by = c("WeppID")) %>% dplyr::rename("wepp_id" = "WeppID")
```

```{r, echo=FALSE, fig.cap="Change in storage (mm) for each hillslope."}
# make_leaflet_map(Hwatbal_spdf, wb,col_pal_type = "Numeric",unit = "mm")

```

#### Composition of streamflow

The figure below shows the total simulated streamflow for each water year divided into baseflow, lateral flow, and runoff, and the percentage of each relative to the streamflow. For the entire simulation period, the average <span class="baseflow">baseflow was `r round(mean(perc_flow$PercentBaseflow))`%</span>, <span class="lateral">lateral flow was `r round(mean(perc_flow$PercentLateral))`%</span>, and <span class="runoff">runoff was `r round(mean(perc_flow$PercentRunoff))`%</span>. 

```{r, echo=FALSE, message=FALSE,warning=FALSE}

perc_flow %>%
      echarts4r::e_charts(x = WY_label) %>%
      echarts4r::e_area(PercentBaseflow, name = "Baseflow (% relative to streamflow)") %>%
      echarts4r::e_area(PercentLateral, name = "Lateral Flow (% relative to streamflow)") %>%
      echarts4r::e_area(PercentRunoff, name = "Runoff (% relative to streamflow)") %>%
      echarts4r::e_tooltip(trigger = "axis")%>%
      echarts4r::e_theme("auritus")%>%
      echarts4r::e_color(c("darkgrey", "red",  "blue"))%>%
      echarts4r::e_axis_labels(
    x = "Water Year",
    y = "Percent relative to streamflow"
  ) %>% echarts4r::e_y_axis(nameTextStyle = list(fontSize = 13))%>%
  echarts4r::e_x_axis(nameTextStyle = list(fontSize = 13))%>%
          echarts4r::e_legend(textStyle = list(fontSize = 14))
```

```{r, echo=FALSE, message=FALSE,warning=FALSE}
runoff_cp_df= gen_cumulative_plt_df(subcatchments, runoff_mm)
sd_yd_cp_df= gen_cumulative_plt_df(subcatchments, Sediment_Yield_kg)

sd_yd_cp_df <- sd_yd_cp_df %>%
  dplyr::arrange(dplyr::desc(Sediment_Yield_kg))

total_sediment_hill <- sum(sd_yd_cp_df$Sediment_Yield_kg, na.rm = TRUE)
total_area_sediment <- sum(sd_yd_cp_df$area_ha, na.rm = TRUE)

if (total_sediment_hill > 0 && total_area_sediment > 0) {
  sd_yd_cp_df <- sd_yd_cp_df %>%
    dplyr::mutate(
      cumPercArea = cumsum(area_ha) / total_area_sediment * 100,
      cum_Sediment_Yield_kg = cumsum(Sediment_Yield_kg) / total_sediment_hill * 100
    )
}

runoff_cp_df <- runoff_cp_df %>%
  dplyr::arrange(dplyr::desc(runoff_mm))

total_runoff_hill <- sum(runoff_cp_df$runoff_mm, na.rm = TRUE)
total_area_hill <- sum(runoff_cp_df$area_ha, na.rm = TRUE)

if (total_runoff_hill > 0 && total_area_hill > 0) {
  runoff_cp_df <- runoff_cp_df %>%
    dplyr::mutate(
      cumPercArea = cumsum(area_ha) / total_area_hill * 100,
      cum_runoff_mm = cumsum(runoff_mm) / total_runoff_hill * 100
    )
}

total_runoff_depth_mm <- sum(totalwatseddf$runoff_mm, na.rm = TRUE)
runoff_raw_rows <- nrow(runoff_cp_df)
runoff_non_missing <- sum(!is.na(runoff_cp_df$runoff_mm))
runoff_cum_na <- sum(is.na(runoff_cp_df$cum_runoff_mm))
runoff_area_na <- sum(is.na(runoff_cp_df$cumPercArea))
runoff_hill_total <- sum(runoff_cp_df$runoff_mm, na.rm = TRUE)

runoff_sample_values <- paste(head(runoff_cp_df$runoff_mm, 5), collapse = ", ")
runoff_cum_samples <- paste(head(runoff_cp_df$cum_runoff_mm, 5), collapse = ", ")
runoff_area_samples <- paste(head(runoff_cp_df$cumPercArea, 5), collapse = ", ")

runoff_cp_stats <- runoff_cp_df %>%
  dplyr::mutate(
    runoff_mm = dplyr::coalesce(runoff_mm, 0),
    cum_runoff_mm = dplyr::coalesce(cum_runoff_mm, 0),
    cumPercArea = dplyr::coalesce(cumPercArea, 0)
  )

if (nrow(runoff_cp_stats) > 0) {
  if (max(runoff_cp_stats$cum_runoff_mm, na.rm = TRUE) <= 1) {
    runoff_cp_stats <- runoff_cp_stats %>%
      dplyr::mutate(cum_runoff_mm = cum_runoff_mm * 100)
  }
  if (max(runoff_cp_stats$cumPercArea, na.rm = TRUE) <= 1) {
    runoff_cp_stats <- runoff_cp_stats %>%
      dplyr::mutate(cumPercArea = cumPercArea * 100)
  }
  runoff_top_slice <- df_head_percent(as.data.frame(runoff_cp_stats), 30)
  runoff_top_pct <- tail(runoff_top_slice$cum_runoff_mm, 1)
  runoff_top_area <- tail(runoff_top_slice$cumPercArea, 1)
  if (!length(runoff_top_pct) || is.na(runoff_top_pct)) {
    runoff_top_pct <- 0
  }
  if (!length(runoff_top_area) || is.na(runoff_top_area)) {
    runoff_top_area <- 0
  }
} else {
  runoff_top_slice <- runoff_cp_stats
  runoff_top_pct <- 0
  runoff_top_area <- 0
}

sd_cp_stats <- sd_yd_cp_df %>%
  dplyr::filter(
    !is.na(Sediment_Yield_kg),
    !is.na(cum_Sediment_Yield_kg),
    !is.na(cumPercArea)
  )
sediment_raw_rows <- nrow(sd_yd_cp_df)
sediment_non_missing <- sum(!is.na(sd_yd_cp_df$Sediment_Yield_kg))

total_sediment_mass <- sum(sd_yd_cp_df$Sediment_Yield_kg, na.rm = TRUE)

if (nrow(sd_cp_stats) > 0) {
  sd_top_slice <- df_head_percent(as.data.frame(sd_cp_stats), 30)
  sd_top_pct <- tail(sd_top_slice$cum_Sediment_Yield_kg, 1)
  sd_top_area <- tail(sd_top_slice$cumPercArea, 1)
  if (!length(sd_top_pct) || is.na(sd_top_pct)) {
    sd_top_pct <- 0
  }
  if (!length(sd_top_area) || is.na(sd_top_area)) {
    sd_top_area <- 0
  }
} else {
sd_top_slice <- sd_cp_stats
  sd_top_pct <- 0
  sd_top_area <- 0
}

debug_runoff_note <- glue::glue("<!-- RUNOFF_DEBUG total={total_runoff_depth_mm} filtered_rows={nrow(runoff_cp_stats)} raw_rows={runoff_raw_rows} non_missing={runoff_non_missing} hill_total={runoff_hill_total} cum_na={runoff_cum_na} area_na={runoff_area_na} samples={runoff_sample_values} cum_samples={runoff_cum_samples} area_samples={runoff_area_samples} top_pct={runoff_top_pct} top_area={runoff_top_area} -->")
debug_runoff_table <- paste(capture.output(utils::head(runoff_cp_df[, c('runoff_mm', 'cum_runoff_mm', 'cumPercArea')])), collapse = " | ")
debug_sediment_note <- glue::glue("<!-- SEDIMENT_DEBUG total={total_sediment_mass} filtered_rows={nrow(sd_cp_stats)} raw_rows={sediment_raw_rows} non_missing={sediment_non_missing} top_pct={sd_top_pct} top_area={sd_top_area} -->")

runoff_cp_stats <- runoff_cp_stats %>% dplyr::mutate(runoff_mm = as.numeric(runoff_mm))
sd_cp_stats <- sd_cp_stats %>% dplyr::mutate(Sediment_Yield_kg = as.numeric(Sediment_Yield_kg))

runoff_map_sf <- runoff_cp_df %>% sf::st_as_sf() %>% sf::st_cast()
sediment_map_sf <- sd_yd_cp_df %>% sf::st_as_sf() %>% sf::st_cast()

render_runoff_map <- nrow(runoff_map_sf) > 0
render_sediment_map <- nrow(sediment_map_sf) > 0

```


### Runoff 

<div id="wrapper">

`r debug_runoff_note`
<!-- `r debug_runoff_table` -->
`r if(total_runoff_depth_mm <= 0) {"<!--"}`

<div class="column-left">

<span class='bigger'>
`r round(runoff_top_pct)`% </span> <span class='big_txt'> `r stringr::str_to_title(stringr::str_split(colnames(runoff_cp_df)[6],"_")[[1]][2])` is generated by
`r round(runoff_top_area)`% watershed area.</span>


`r if(total_runoff_depth_mm <= 0) {"-->"}`

`r if(total_runoff_depth_mm <= 0) {"<span class='big_txt'>No runoff was generated during the entire simulation.</span>"}`

</div>

<div class="column-center"> </div>

<div class="column-right">

```{r, echo=FALSE, message=FALSE,warning=FALSE}
          
gp_runoff = runoff_cp_stats %>%
  echarts4r::e_charts(x = cumPercArea) %>%
  echarts4r::e_area(cum_runoff_mm, name = stringr::str_to_title(stringr::str_split(colnames(runoff_cp_df)[6],"_")[[1]][2]))%>%
  echarts4r::e_tooltip(trigger = "axis")%>%
  e_theme("sakura")%>%
  e_axis_labels(x="Area (%)",
                y = paste(stringr::str_to_title(stringr::str_split(colnames(runoff_cp_df)[6],"_")[[1]][2]), "(%)", sep = " "))%>% echarts4r::e_y_axis(nameTextStyle = list(fontSize = 13))%>%
  echarts4r::e_x_axis(nameTextStyle = list(fontSize = 13))%>%
          echarts4r::e_legend(textStyle = list(fontSize = 14))


gp_runoff
          
```      
</div>

</div>

<!-- ######################### Runoff Plot and Table ################################# -->

<div style="clear: both;"></div>

```{r, echo=FALSE, message=FALSE,warning=FALSE}
# Wrap data frame in SharedData
sd_r= runoff_map_sf
sd_r <- SharedData$new(sd_r)
#
```



<div style="clear: both;"></div>

<div id="wrapper-two">

<div id="map-canvas">

```{r echo=FALSE}

# # Create a filter input
filter_slider("cumPercArea", "Filter map and table by watershed area(%) that generates most runoff. ", sd_r, column=~cumPercArea, step=1, width=600)
```
<span style='color: #8e9aaf;'>(Known bug: Legend might disappear on filtering, please reload the page to get the legend back.)</span>
```{r echo=FALSE}
if (render_runoff_map && nrow(sd_r$data()) > 0) {
  ggplotly(
    ggplot() +
      geom_sf(data = sd_r, mapping = aes(fill = runoff_mm), show.legend = TRUE) +
      coord_sf() +
      labs(fill = "Runoff (mm)") +
      ggthemes::theme_map() +
      scale_fill_viridis_c(option = "A", alpha = 0.9)
  ) %>% plotly::layout(legend = TRUE)
} else {
  htmltools::HTML("<p class='big_txt'>Runoff map unavailable for this run.</p>")
}


```
</div>
<div id="tab-canvas">
```{r echo=FALSE}

DT::datatable(sd_r,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                           scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
                           fillContainer = FALSE,
                           columnDefs = list(list(className = 'dt-left',
                                                  width = '100%',visible=FALSE,
                                                  targets=c(3:4,9)))),
               rownames= FALSE)%>%
  formatStyle(
    'runoff_mm',
    background = styleColorBar(sd_r$data()$runoff_mm, '#ED6A76'),
    backgroundSize = '90% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```
</div>
</div>

<div style="clear: both;"></div>
<!-- ##############################Sediment###################################### -->

### Sediments

<div style="clear: both;"></div>

`r debug_sediment_note`

<div class="column-cntr-plt-and-tab"> </div>
<div id="wrapper">

<div class="column-right-alt">

`r if(total_sediment_mass <= 0) {"<!--"}`

<span class='bigger'>`r round(sd_top_pct)`% </span> <span class='big_txt'> `r stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][2]` `r stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][3]` is contributed by
`r round(sd_top_area)`% watershed area.</span>

`r if(total_sediment_mass <= 0) {"-->"}`

`r if(total_sediment_mass <= 0) {"<span class='big_txt'>No sediment was generated during the entire simulation.</span>"}`
`r if(total_sediment_mass <= 0) {debug_sediment_note}`

</div>

<div class="column-center"> </div>

<div class="column-left-alt">

```{r, echo=FALSE, message=FALSE,warning=FALSE}
          
gp_sed = sd_cp_stats %>%
  echarts4r::e_charts(x = cumPercArea) %>%
  echarts4r::e_area(cum_Sediment_Yield_kg,
  name=paste(stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][2], stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][3], sep = " "))%>%
                echarts4r::e_tooltip(trigger = "axis")%>%e_theme("sakura")%>%
            e_axis_labels(x="Area (%)",
                          y= paste(stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][2], stringr::str_split(colnames(sd_yd_cp_df)[6],"_")[[1]][3], "(%)", sep = " "))%>% echarts4r::e_y_axis(nameTextStyle = list(fontSize = 13))%>%
  echarts4r::e_x_axis(nameTextStyle = list(fontSize = 13))%>%
          echarts4r::e_legend(textStyle = list(fontSize = 14))

gp_sed
          
``` 
<div style="clear: both;"></div>   
</div>
</div>

<!-- ######################### Sediment Plot and Table ################################# -->

<div style="clear: both;"></div>

```{r, echo=FALSE, message=FALSE,warning=FALSE}
# Wrap data frame in SharedData
sd= sediment_map_sf
sd <- SharedData$new(sd)
```

<div id="wrapper-two">

<div id="map-canvas">
```{r echo=FALSE}

# # Create a filter input
filter_slider("cumPercArea", "Filter map and table by watershed area(%) that generates most sediments.", sd, column=~cumPercArea, step=1, width=600)
```

<span style='color: #8e9aaf;'>(Known bug: Legend might disappear on filtering, please reload the page to get the legend back.)</span>
```{r echo=FALSE}
if (render_sediment_map && nrow(sd$data()) > 0) {
  ggplotly(
    ggplot() +
      geom_sf(data = sd, mapping = aes(fill = Sediment_Yield_kg), show.legend = TRUE) +
      coord_sf() +
      labs(fill = "Sediment Yield (kg)") +
      ggthemes::theme_map() +
      scale_fill_viridis_c(option = "A", alpha = 0.9)
  )
} else {
  htmltools::HTML("<p class='big_txt'>Sediment map unavailable for this run.</p>")
}


```

</div>

<div id="tab-canvas">
```{r echo=FALSE}

DT::datatable(sd,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                           scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
                           fillContainer = FALSE,
                           columnDefs = list(list(className = 'dt-left',
                                                  width = '100%',visible=FALSE,
                                                  targets=c(3:4,9)))),
               rownames= FALSE)%>%
  formatStyle(
    'Sediment_Yield_kg',
    background = styleColorBar(sd$data()$Sediment_Yield_kg, '#ED6A76'),
    backgroundSize = '90% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```
</div>
</div>


```{r echo=FALSE}
has_phosphorus <- any(subcatchments$Total_Phosphorus_kg > 0, na.rm = TRUE) ||
  any(subcatchments$tp_kg_ha > 0, na.rm = TRUE)
if (has_phosphorus) {
  tp_cp_df <- gen_cumulative_plt_df(subcatchments, Total_Phosphorus_kg)
}
```

### Total Phosphorus


<div style="clear: both;"></div>
<div id="wrapper">
            
<div class="column-left">

```{r echo=FALSE, eval=has_phosphorus}

if(sum(tp_cp_df$Total_Phosphorus_kg)==0) {
  htmltools::HTML("<span class='big_txt'>No phosphorus was generated during the entire simulation.</span>")
} else {
  htmltools::HTML(paste("<span class='bigger'>",
        round(tail(df_head_percent(as.data.frame(tp_cp_df), 30),1)[,6]), " % </span> <span class='big_txt'>",
        stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][2], stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][3],
        " is contributed by", round(tail(df_head_percent(as.data.frame(tp_cp_df), 30),1)[,5]), "% watershed area. </span>"))
}

```
</div>

<div class="column-center"> </div>


<div class="column-right">

```{r echo=FALSE, eval=has_phosphorus}

gp_tp = tp_cp_df %>%
  echarts4r::e_charts(x = cumPercArea) %>%
  echarts4r::e_area(cum_Total_Phosphorus_kg,
                     name = paste(stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][2], stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][3], sep = " "))%>%
  echarts4r::e_tooltip(trigger = "axis")%>%
  e_theme("sakura")%>%
  e_axis_labels(x = "Area (%)",
                y = paste(stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][2], stringr::str_split(colnames(tp_cp_df)[6],"_")[[1]][3], "(%)", sep = " "))%>%
  echarts4r::e_y_axis(nameTextStyle = list(fontSize = 13))%>%
  echarts4r::e_x_axis(nameTextStyle = list(fontSize = 13))%>%
  echarts4r::e_legend(textStyle = list(fontSize = 14))

gp_tp

```
</div>

<!-- ######################### TP Plot and Table ################################# -->

<div style="clear: both;"></div>

```{r echo=FALSE, eval=has_phosphorus}
# Wrap data frame in SharedData
sd_tp= tp_cp_df %>% sf::st_as_sf() %>% sf::st_cast()
sd_tp <- SharedData$new(sd_tp)
```

<div id='wrapper-two'>
<div id='map-canvas'>
<div style='clear: both;'></div>

```{r, echo=FALSE, message=FALSE,warning=FALSE,eval=has_phosphorus}
# # Create a filter input
filter_slider("cumPercArea", "Filter map and table by watershed area(%) that generates most phosphorus.", sd_tp, column=~cumPercArea, step=1, width=600)
```


<span style='color: #8e9aaf;'>(Known bug: Legend might disappear on filtering, please reload the page to get the legend back.)</span>


```{r, echo=FALSE, message=FALSE,warning=FALSE,eval=has_phosphorus}

ggplotly(ggplot() +
    geom_sf(data = sd_tp, mapping = aes(fill = Total_Phosphorus_kg), show.legend = TRUE)  +coord_sf()+labs(fill = "Total Phosphorus (kg)") +ggthemes::theme_map()+scale_fill_viridis_c(option = "A",alpha = 0.9))

```

</div>

<div id="tab-canvas">
```{r echo=FALSE,eval=has_phosphorus}

DT::datatable(sd_tp,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                           scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
                           fillContainer = FALSE,
                           columnDefs = list(list(className = 'dt-left',
                                                  width = '100%',visible=FALSE,
                                                  targets=c(3:4,9)))),
               rownames= FALSE)%>%
  formatStyle(
    'Total_Phosphorus_kg',
    background = styleColorBar(sd_tp$data()$Total_Phosphorus_kg, '#ED6A76'),
    backgroundSize = '90% 100%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )
```
</div>
</div>



### Timeseries plots
            
#### Daily
<div style="clear: both;"></div>

          
```{r, echo=FALSE, message=FALSE,warning=FALSE}
daily_plt_precip = merged_daily_df %>% 
  dplyr::select(dplyr::any_of(c("Date","precipitation_mm")))

merged_daily_df_plt = merged_daily_df %>% dplyr::select(dplyr::any_of(c("Date", "Q_outlet_mm",
                                                            "Sediment_tonnes_ebe"))) %>%
    plyr::rename( c("Q_outlet_mm" ="Streamflow (mm)",
                   "Sediment_tonnes_ebe"="Sediments (Mg)"),
                  warn_missing = FALSE)%>% reshape2::melt(id.vars = "Date")

```

#### Precipitation, Streamflow,  Sediment Yield timeseries
          
```{r, echo=FALSE, message=FALSE,warning=FALSE}
PrecipAx_d <- list(
       overlaying = "y",
       side = "right",
       title = "Precipitation (mm)",
       range = c(max(daily_plt_precip$precipitation_mm)*2.5,0),
       showgrid=FALSE, automargin = TRUE, color = "#7fc8f8"
   )
fig = plot_ly(colors = c("#a17c6b", "#ff6392")) %>% 
  plotly::add_trace(x = ~Date, y = ~value, color = ~variable, data = merged_daily_df_plt,
                                        type = "scatter", mode= "line")%>%
  plotly::add_trace(x = ~Date, y = ~precipitation_mm, data = daily_plt_precip,
                  type = "scatter", mode= "line", yaxis="y2",
                  name="Precipitation (mm)",
                  line=list(color='#5aa9e6')) %>% 
  layout(yaxis2=PrecipAx_d,legend = list(orientation = "h", x=0.05, y = 1.15,
                                         font = list( size = 16, color = "black")), yaxis = list(title = ""))
fig

```

#### Phosphorus timeseries

```{r, echo=FALSE, message=FALSE,warning=FALSE,eval=has_phosphorus} 

  merged_daily_P_df_plt = merged_daily_df %>% dplyr::select(dplyr::any_of(c("Date", "SRP_tonnes_ebe",
                                          "PP_tonnes_ebe",
                                          "TP_tonnes_ebe"))) %>%
    plyr::rename( c("SRP_tonnes_ebe"="SRP (Mg)",
                   "PP_tonnes_ebe" ="PP (Mg)" ,
                   "TP_tonnes_ebe" ="TP (Mg)"),
                  warn_missing = FALSE)%>% reshape2::melt(id.vars = "Date")


fig2 = plot_ly(colors = "viridis") %>% 
  plotly::add_trace(x = ~Date, y = ~value, color = ~variable, data = merged_daily_P_df_plt,
                                        type = "scatter", mode= "line")
fig2

```


### Summary tables

#### Grouped by land use

The table below shows runoff, sediment and phosphorus averages for different land use categories.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
landuse_summary_tab <- subcatchments %>%
  sf::st_drop_geometry() %>%
  dplyr::select(dplyr::any_of(c("landuse", "slope",
                                "runoff_mm", "so_ls_kg_ha",
                                "sd_yd_kg_ha", "tp_kg_ha"))) %>%
  dplyr::rename(
    Landuse = landuse,
    Slope = slope,
    `Soil Loss (kg/ha)` = so_ls_kg_ha,
    `Sediment Yield (kg/ha)` = sd_yd_kg_ha,
    `Total Phosphorus (kg/ha)` = tp_kg_ha,
    `Runoff (mm)` = runoff_mm
  ) %>%
  dplyr::group_by(Landuse) %>%
  dplyr::summarise(
    dplyr::across(
      where(is.numeric),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    .groups = "drop"
  ) %>%
  dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2)))

```

```{r, echo=FALSE}
DT::datatable(landuse_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           searching = FALSE,
                           scrollX=400,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```


#### Grouped by soils

The table below shows runoff, sediment and phosphorus averages for different soil types.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
soils_summary_tab <- subcatchments %>%
  sf::st_drop_geometry() %>%
  dplyr::select(dplyr::any_of(c("soil", "slope",
                                "runoff_mm", "so_ls_kg_ha",
                                "sd_yd_kg_ha", "tp_kg_ha"))) %>%
  dplyr::rename(
    Soil = soil,
    Slope = slope,
    `Soil Loss (kg/ha)` = so_ls_kg_ha,
    `Sediment Yield (kg/ha)` = sd_yd_kg_ha,
    `Total Phosphorus (kg/ha)` = tp_kg_ha,
    `Runoff (mm)` = runoff_mm
  ) %>%
  dplyr::group_by(Soil) %>%
  dplyr::summarise(
    dplyr::across(
      where(is.numeric),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    .groups = "drop"
  ) %>%
  dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2)))

```

```{r, echo=FALSE}
DT::datatable(soils_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=250,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```

#### Grouped by texture

The table below shows runoff, sediment and phosphorus averages for different soil textures.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
texture_summary_tab <- subcatchments %>%
  sf::st_drop_geometry() %>%
  dplyr::select(dplyr::any_of(c("Texture", "slope",
                                "runoff_mm", "so_ls_kg_ha",
                                "sd_yd_kg_ha", "tp_kg_ha"))) %>%
  dplyr::rename(
    Slope = slope,
    `Soil Loss (kg/ha)` = so_ls_kg_ha,
    `Sediment Yield (kg/ha)` = sd_yd_kg_ha,
    `Total Phosphorus (kg/ha)` = tp_kg_ha,
    `Runoff (mm)` = runoff_mm
  ) %>%
  dplyr::group_by(Texture) %>%
  dplyr::summarise(
    dplyr::across(
      where(is.numeric),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    .groups = "drop"
  ) %>%
  dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2)))

```

```{r, echo=FALSE}
DT::datatable(texture_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=250,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```

#### Grouped by landuse and soils type and texture.

The table below shows runoff, sediment and phosphorus averages for different combinations of land use categories and soil types.

```{r, echo=FALSE, message=FALSE,warning=FALSE}
both_summary_tab <- subcatchments %>%
  sf::st_drop_geometry() %>%
  dplyr::select(dplyr::any_of(c("landuse", "soil", "Texture", "slope",
                                "runoff_mm", "so_ls_kg_ha",
                                "sd_yd_kg_ha", "tp_kg_ha"))) %>%
  dplyr::rename(
    Landuse = landuse,
    Soil = soil,
    Slope = slope,
    `Soil Loss (kg/ha)` = so_ls_kg_ha,
    `Sediment Yield (kg/ha)` = sd_yd_kg_ha,
    `Total Phosphorus (kg/ha)` = tp_kg_ha,
    `Runoff (mm)` = runoff_mm
  ) %>%
  dplyr::group_by(Landuse, Soil, Texture) %>%
  dplyr::summarise(
    dplyr::across(
      where(is.numeric),
      ~ mean(.x, na.rm = TRUE),
      .names = "{.col}"
    ),
    .groups = "drop"
  ) %>%
  dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 2)))

```

```{r, echo=FALSE}
DT::datatable(both_summary_tab,
              class = "display",
              extensions=c("Scroller","Buttons"),
              options=list(dom = 'BRSfrti',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           deferRender=TRUE,
                           scrollX=400,
                          scrollY=250,
                           scroller=TRUE,
                           autoWidth = TRUE,
                           fixedHeader = FALSE,
            fillContainer = FALSE),
               rownames= FALSE)

  
```
