---
title: "`r paste0('A report generated for', ' PLACEHOLDER', ' WEPPcloud run')`"
date: "`r Sys.Date()`"
output: 
  cleanrmd::html_document_clean:
    theme: axist
    mathjax: default
    use_fontawesome: true
    toc: true
    toc_float: true
params:
  proj_runid: default 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
# install.packages("devtools")
# devtools::install_github("gadenbuie/cleanrmd")
library(tidyverse, quietly = TRUE)
library(cleanrmd, quietly = TRUE)
library(plotly, quietly = TRUE)
library(furrr, quietly = TRUE)
library(janitor, quietly = TRUE)
library(cleanrmd, quietly = TRUE)
library(echarts4r, quietly = TRUE)
library(DT, quietly = TRUE)
library(leaflet, quietly = TRUE)
library(data.table, quietly = TRUE)


```


<!-- ################################## FUNCTIONS AND PROCESSING #####################-->


```{r, echo=FALSE}
### spdf
gethillwatfiles<- function(runid){
  link <- paste0("/geodata/weppcloud_runs/", runid,"/wepp/output/")
  wat_dat <- list.files(link, "*\\.wat.dat$", full.names=TRUE)
  return(wat_dat)
}

calc_watbal <- function(link){
  a <- read.table(link, skip = 23,
                  col.names = c("OFE",	"J",	"Y",	"P",	"RM",	"Q",	"Ep",	"Es",
                                "Er",	"Dp",	"UpStrmQ",	"SubRIn",	"latqcc",
                                "Total_Soil_Water",	"frozwt",	"Snow_Water",	"QOFE",
                                "Tile",	"Irr",	"Area")) %>%
    dplyr::mutate_if(is.character,as.numeric)
  
  
  a <- a %>%  dplyr::mutate(wb = P-Q-Ep - Es- Er - Dp - latqcc +
                              dplyr::lag(Total_Soil_Water) - Total_Soil_Water +
                              dplyr::lag(frozwt) - frozwt+ dplyr::lag(Snow_Water) - Snow_Water) %>%
    dplyr::mutate(dplyr::across(where(is.numeric), round, 3)) %>% dplyr::select(wb) %>%
    dplyr::summarise_all(.funs = sum, na.rm = TRUE) %>%
    dplyr::mutate(WeppID =readr::parse_number(gsub("^.*/", "", link)))
  
  return(as.data.frame(a))
}

get_geometry <- function(runid){
  link <- paste0("/geodata/weppcloud_runs/", params$proj_runid, "/export/arcmap/subcatchments.json")
  geometry <- sf::st_read(link,quiet = TRUE)%>%
    dplyr::select(WeppID, geometry) %>%
    sf::st_transform(4326) %>%
    dplyr::group_by(WeppID)%>%
    dplyr::summarize(geometry = sf::st_union(geometry))

  return(geometry)
  
}
```

```{r echo= FALSE}
## channel water balance
get_WatershedArea_m2 <- function(file){
  getstring<- grep("Total contributing area to outlet ",
                   readLines(file), value = TRUE)
  getstring <- getstring[[1]]
  num <- readr::parse_number(getstring)
  num <- as.numeric(num) * 10000 ##convert ha to m2
  return(num)

}

get_WY <- function(x, numeric=TRUE) {
  x <- as.POSIXlt(x)
  yr <- x$year + 1900L
  mn <- x$mon + 1L
  ## adjust for water year
  yr <- yr + ifelse(mn < 10L, 0L, 1L)
  if(numeric)
    return(yr)
  ordered(yr)
}
 

process_chanwb <- function(chanwb_path, Wshed_Area_m2){

  ## read channel and watershed water and sediment data

  chanwb <- data.table::fread(chanwb_path, skip = 11, header = F)

  ### set names of the dataframes

  colnames(chanwb) <- c("Year_chan", "Day_chan", "Elmt_ID_chan",
                        "Chan_ID_chan", "Inflow_chan", "Outflow_chan",
                        "Storage_chan", "Baseflow_chan", "Loss_chan",
                        "Balance_chan")



  chanwb <- chanwb %>% dplyr::mutate(Q_outlet_mm = (Outflow_chan/ Wshed_Area_m2 *1000),
                                     originDate = as.Date(paste0(Year_chan, "-01-01"),tz = "UTC") - lubridate::days(1),
                                     Date = as.Date(Day_chan, origin = originDate, tz = "UTC"),
                                     WY = get_WY(Date)) %>% dplyr::select(-originDate) %>%
    dplyr::select(Year_chan, Day_chan, Date, WY, everything())



  return(as.data.frame(chanwb))

}


```

```{r, echo=FALSE}
wshed_area_m2= get_WatershedArea_m2(paste0(
          "/geodata/weppcloud_runs/",
          params$proj_runid,
          "/wepp/output/",
          "loss_pw0.txt"
        ))
```




```{r, echo=FALSE}
# Event by event file
 
process_ebe <- function(ebe_path, yr_start, yr_end){

  ## read channel and watershed water and sediment data
# , SimStartDate, SimEndDate, SimStartDate, SimEndDate
  ebe <- data.table::fread(ebe_path, skip = 9, header = F)

  ### set names of the dataframe

  colnames(ebe) <- c("Day_ebe", "Month_ebe", "Year_ebe",
                     "P_ebe", "Runoff_ebe", "peak_ebe", "Sediment_ebe",
                     "SRP_ebe", "PP_ebe", "TP_ebe")
  
  dt_head_d = as.character(head(ebe,1)[[1]])
  dt_head_m = as.character(head(ebe,1)[[2]])
  dt_tail_d = as.character(tail(ebe,1)[[1]])
  dt_tail_m = as.character(tail(ebe,1)[[2]])

  # calcs
  ebe <- ebe %>% dplyr::mutate(Date = seq(from = as.Date(paste0(yr_start,"-",dt_head_m,"-",dt_head_d)), 
                                          to = as.Date(paste0(yr_end,"-",dt_tail_m,"-",dt_tail_d)), by= 1),
                               WY = get_WY(Date),
                               Sediment_tonnes_ebe = Sediment_ebe/1000,
                               SRP_tonnes_ebe = SRP_ebe/1000,
                               PP_tonnes_ebe = PP_ebe/1000,
                               TP_tonnes_ebe = TP_ebe/1000) %>%
    dplyr::select(Day_ebe, Month_ebe, Year_ebe, Date, WY, everything())



  return(as.data.frame(ebe))

}
```



<!-- ############################ PREP DATA ######################################-->


```{r echo=FALSE,message=FALSE,warning=FALSE}
### totalwatsed

totalwatsed_fn = paste0("/geodata/weppcloud_runs/", params$proj_runid, "/export/totalwatsed.csv")

if (file.exists(totalwatsed_fn)) {
    totalwatseddf <- data.table::fread(totalwatsed_fn)
} else {
    totalwatseddf <- data.table::fread(paste0("https://wepp.cloud/weppcloud/runs/", params$proj_runid, "/cfg/resources/wepp/totalwatsed.csv"))
}

```


```{r echo=FALSE,message=FALSE,warning=FALSE}
### totalwatsed
totalwatseddf = totalwatseddf %>% 
  janitor::clean_names()%>%
  dplyr::rename("WY" = "water_year")%>%
  dplyr::mutate(Date = lubridate::make_date(year,mo,da))


totalwatsed_wy_mean_df = totalwatseddf %>%
          dplyr::select(-julian,-year,-Date,-mo,-da) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise_all(mean)


totalwatsed_wbal = totalwatseddf %>% dplyr::select(
              "WY",
              "Date",
              "precipitation_mm",
              "rain_melt_mm",
              "transpiration_mm",
              "evaporation_mm",
              "percolation_mm",
              "runoff_mm",
              "lateral_flow_mm"
          )%>% dplyr::filter(Date >= paste0(lubridate::year(Date[1]),"-10-01"))
wys = as.numeric(length(unique(totalwatsed_wbal$WY)))

totalwatsed_wbal= totalwatsed_wbal %>%
  dplyr::select(- c(Date,WY))%>%
          dplyr::summarise_all(.funs = sum) %>%
          dplyr::mutate(
              precipitation_mm = precipitation_mm / wys,
              rain_melt_mm = rain_melt_mm / wys,
              transpiration_mm = transpiration_mm / wys,
              evaporation_mm = evaporation_mm / wys,
              percolation_mm = percolation_mm / wys,
              runoff_mm = runoff_mm / wys,
              lateral_flow_mm = lateral_flow_mm / wys) %>%
          dplyr::mutate(
              rain_melt_mm = rain_melt_mm / precipitation_mm * 100,
              transpiration_mm = transpiration_mm / precipitation_mm *
                  100,
              evaporation_mm = evaporation_mm / precipitation_mm *
                  100,
              percolation_mm = percolation_mm / precipitation_mm *
                  100,
              runoff_mm = runoff_mm / precipitation_mm * 100,
              lateral_flow_mm = lateral_flow_mm / precipitation_mm *
                  100,
              WbalErr_mm = rain_melt_mm - (
                  transpiration_mm + evaporation_mm + percolation_mm + runoff_mm + lateral_flow_mm
              )
          ) %>%
          dplyr::rename(
              "Precipitation (mm)" = "precipitation_mm",
              "Rain+Melt (%)" = "rain_melt_mm",
              "Transpiration (%)" = "transpiration_mm",
              "Evaporation (%)" = "evaporation_mm",
              "Percolation (%)" = "percolation_mm",
              "Runoff(%)" = "runoff_mm",
              "Lateral flow(%)" = "lateral_flow_mm",
              "Water Balance Error(%)" = "WbalErr_mm"
          ) %>%
          tidyr::gather(key = "variable") %>% 
  dplyr::mutate(dplyr::across(where(is.numeric), round, 2))
    
```



```{r, echo=FALSE}
chanwb = process_chanwb(
                  paste0("/geodata/weppcloud_runs/",
                      params$proj_runid,
                      "/wepp/output/",
                      "chanwb.out"
                  ),
                  wshed_area_m2
              )

chanwb_WY_mean = chanwb %>%
          dplyr::select(-Year_chan,
                        -Day_chan,
                        -Chan_ID_chan,
                        -Elmt_ID_chan,
                        -Date) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise_all(mean)
```

```{r, echo=FALSE}
yr_min= as.character(min(unique(chanwb$Year_chan)))
yr_max= as.character(max(unique(chanwb$Year_chan)))
```

```{r, echo=FALSE}
ebe = process_ebe(paste0("/geodata/weppcloud_runs/",
                      params$proj_runid,
                      "/wepp/output/",
                      "ebe_pw0.txt"
                  ),
                  yr_min,
                  yr_max)

ebe_WY_mean = ebe %>%
          dplyr::select(-Date,-Day_ebe,-Month_ebe,-Year_ebe) %>%
          dplyr::group_by(WY) %>%
          dplyr::summarise_all(mean)
```

```{r, echo=FALSE}
merge_daily_Vars <- function(totalwatsed_df, chanwb_df, ebe_df){
  daily<- dplyr::left_join(as.data.frame(totalwatsed_df), as.data.frame(chanwb_df), by = c("Date", "WY")) %>%
    dplyr::left_join(as.data.frame(ebe_df),  by = c("Date", "WY")) %>%
    dplyr::mutate_at(c("area_m_2",	"precip_vol_m_3",	"rain_melt_vol_m_3",	"transpiration_vol_m_3",
                "evaporation_vol_m_3",	"percolation_vol_m_3",	"runoff_vol_m_3",	"lateral_flow_vol_m_3",
                "storage_vol_m_3",	"sed_det_kg",	"sed_dep_kg",	"sed_del_kg",
                "class_1",	"class_2",	"class_3",	"class_4",	"class_5",
                "area_ha",	"cumulative_sed_del_tonnes",	"sed_del_density_tonne_ha",
                "precipitation_mm",	"rain_melt_mm",	"transpiration_mm",	"evaporation_mm",	"et_mm",
                "percolation_mm",	"runoff_mm",	"lateral_flow_mm",	"storage_mm",
                "reservoir_volume_mm",	"baseflow_mm",	"aquifer_losses_mm",
                "streamflow_mm",	"swe_mm",	"sed_del_tonne",	"p_load_mg",
                "p_runoff_mg",	"p_lateral_mg",	"p_baseflow_mg",	"total_p_kg",
                "particulate_p_kg",	"soluble_reactive_p_kg",	"p_total_kg_ha",	"particulate_p_kg_ha",
                "soluble_reactive_p_kg_ha",	"Elmt_ID_chan",	"Chan_ID_chan",	"Inflow_chan",	"Outflow_chan",
                "Storage_chan",	"Baseflow_chan",	"Loss_chan",	"Balance_chan",
                "Q_outlet_mm",	"Day_ebe",	"P_ebe",	"Runoff_ebe",	"peak_ebe",
                "Sediment_ebe",	"SRP_ebe",	"PP_ebe",	"TP_ebe",
                "Sediment_tonnes_ebe",	"SRP_tonnes_ebe",	"PP_tonnes_ebe",
                "TP_tonnes_ebe"),as.numeric)
  return(daily)
}
```

```{r, echo=FALSE}
merged_daily_df = merge_daily_Vars(totalwatseddf, chanwb, ebe)
merged_WY = dplyr::left_join(totalwatsed_wy_mean_df, chanwb_WY_mean, by = c("WY")) %>%
          dplyr::left_join(ebe_WY_mean, by = c("WY")) %>%
          dplyr::mutate(PercentRunoff = runoff_mm / Q_outlet_mm * 100,
                        PercentLateral = lateral_flow_mm / Q_outlet_mm *100,
                        PercentBaseflow = baseflow_mm / Q_outlet_mm *100)

perc_flow = merged_WY %>%
          dplyr::select(WY, PercentRunoff, PercentLateral, PercentBaseflow)%>% dplyr::mutate(WY = as.Date(paste0(WY,"-12-31")))
```



<!-- ################################# GENERATE REPORT ############################################-->

## Dominant Land Cover & Soil Type 

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r echo=FALSE, warning=FALSE, message=FALSE}

watfilepaths <- gethillwatfiles(params$proj_runid)
future::plan(multisession, workers = 6)
watbal<- furrr::future_map(watfilepaths, calc_watbal)%>%
  dplyr::bind_rows() %>%
  dplyr::mutate_if(is.list, purrr::simplify_all) %>%
  tidyr::unnest(cols = c("wb", "WeppID"))
shp <- get_geometry(proj_runid)
Hwatbal_spdf = dplyr::left_join(shp, watbal, by = c("WeppID"))

```


## Water Balance:

### Watershed scale water balance
Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}
totalwatsed_wbal %>% dplyr::filter(variable != "Precipitation (mm)")  %>%
            echarts4r::e_charts(variable)  %>%
            echarts4r::e_pie(
                value,
                # roseType = "radius",
                radius = c("55%", "70%"),
                # legend = FALSE,
                # hoverAnimation = TRUE
            )%>%
          echarts4r::e_tooltip(
                # formatter = e_tooltip_item_formatter("percent")
            )
```


#### Table

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}
DT::datatable(totalwatsed_wbal)
```

### Water balance at hillslopes

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}
pal <- leaflet::colorNumeric("viridis", domain = Hwatbal_spdf$wb)


leaflet::leaflet(Hwatbal_spdf) %>%
        leaflet::addProviderTiles(leaflet::providers$Esri.WorldTopoMap) %>%
                      leaflet::addPolygons(fillColor = ~pal(wb),
                                           weight = 2,
                                           opacity = 1,
                                           color = "white",
                                           dashArray = "3",
                                           fillOpacity = 0.7,
                                           popup = ~paste("Hillslope ID:", Hwatbal_spdf$WeppID,
                                                          "<br>","Total Water Balance Error (mm):", Hwatbal_spdf$wb),
                                           label = ~WeppID,
                                           highlightOptions = leaflet::highlightOptions(
                                             weight = 5,
                                             color = "#666",
                                             dashArray = "",
                                             fillOpacity = 0.7,
                                             bringToFront = TRUE))%>% leaflet::addLegend(pal = pal,
                                                                         values = ~wb)
```


## Contribution to streamflow

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}

perc_flow %>%
      echarts4r::e_charts(x = WY) %>%
      echarts4r::e_area(PercentBaseflow) %>%
      echarts4r::e_area(PercentLateral) %>%
      echarts4r::e_area(PercentRunoff) %>%
      echarts4r::e_tooltip(trigger = "axis")
```

<!-- "https://wepp.cloud/weppcloud/runs/lt_202012_26_Bliss_Creek_CurCond/lt-wepp_bd16b69-snow/" -->

## WY SWE plot

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}
merged_WY %>%
  dplyr::select(WY, swe_mm ) %>% 
  dplyr::mutate(WY = as.Date(paste0(WY,"-12-31")))%>%
  dplyr::filter(complete.cases(.)) %>%
  echarts4r::e_charts(WY) %>%
  echarts4r::e_line(swe_mm, name = "Simulated") %>%
  echarts4r::e_tooltip(trigger = "axis") %>%
  echarts4r::e_datazoom(x_index = 0, type = "slider") %>%
  echarts4r::e_datazoom(y_index = 0, type = "slider")
```

## Daily Timeseries plot

Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged

```{r, echo=FALSE}
merged_daily_df %>%
  echarts4r::e_charts(Date) %>%
  echarts4r::e_line(Q_outlet_mm, name = "Simulated") %>%
  echarts4r::e_tooltip(trigger = "axis") %>%
  echarts4r::e_datazoom(x_index = 0, type = "slider") %>%
  echarts4r::e_datazoom(y_index = 0, type = "slider")
```

<!-- ## Crosstalk with table and plot -->

<!-- Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged -->

```{r, echo=FALSE}
# hwb_shared = crosstalk::SharedData$new(Hwatbal_spdf, key = ~WeppID, group = "maphwb")
```

```{r, echo=FALSE}
# leafletmap using shared data
# wbmap= leaflet::leaflet(hwb_shared) %>%
#         leaflet::addProviderTiles(leaflet::providers$Esri.WorldTopoMap) %>%
#                       leaflet::addPolygons(fillColor = ~pal(wb),
#                                            weight = 2,
#                                            opacity = 1,
#                                            color = "white",
#                                            dashArray = "3",
#                                            fillOpacity = 0.7,
#                                            popup = ~paste("Hillslope ID:", hwb_shared$WeppID,
#                                                           "<br>","Total Water Balance Error (mm):", hwb_shared$wb),
#                                            label = ~WeppID,
#                                            highlightOptions = leaflet::highlightOptions(
#                                              weight = 5,
#                                              color = "#666",
#                                              dashArray = "",
#                                              fillOpacity = 0.7,
#                                              bringToFront = TRUE))%>% leaflet::addLegend(pal = pal,
#                                                                          values = ~wb)
# 
# wbtab= DT::datatable(hwb_shared)
# wbmap
# wbtab
```

